Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-05-29 paper/icsme20.tex
spellcheck t2v

\section{Threats to Validity}\label{sec:threats}
%
This section presents the potential threats to the validity.
%
\\\textit{\textbf{Construct:}} The formula was inferred based 
on the BCH's reports. The high amount of different projects and backgrounds 
may require other maintainability standards. However, BCH does use a 
representative benchmark of closed and open-source software projects to compute 
the thresholds for each maintainability guideline~\cite{Visser:2016:OREILLY, Baggen2012}.
Maintainability is computed as the mean of all guidelines. Different software versions (vulnerable/fixed) of one vulnerability may have the same overal score
and still be affected by different guidelines.
%
\\\textit{\textbf{Internal:}} The security patches dataset provided by previous
work~\cite{Reis:2017:IJSSE} was collected based on the messages of GitHub
commits produced by project developers to classify the changes performed while patching vulnerabilities. This approach discards patches that were
not explicit in commits messages. We assume that patches were performed 
using a single-commit or several sequentially. The view that a 
developer may perform a patch quickly and later proceed to the refactor is not considered.
Baseline commits are retrieved randomly from the same project of the security patch.
This approach softens the differences
that may result from the characteristics of each project. However,
maintainability may still be affected by the developers' experience, coding
style and software contribution policies which is not evaluated in this study.
Furthermore, this evaluation considers that $969$ regular commits---any kind
of commit---are enough to
alleviate random irregularities in the maintainability differences of the
baseline. 
%
\\\textit{\textbf{External:}} We use a dataset that only comprises patches of open-source software.
However, the methodology requires to access data that is not publicly available.
Thus, our findings may not extend to non-open source software. Different programming 
languages may require different coding practices to address software safety. The 
dataset comprises more commits in Java, i.e., the dataset may not be representative 
of the population regarding programming languages. Our approach does not consider patches in any other languages but English.

>>>>

\section{Threats to Validity}\label{sec:threats}
%
This section presents the potential threats to validity.
%
\\\textit{\textbf{Construct:}} The formula was inferred based 
on the BCH's reports. The high amount of different projects and backgrounds 
may require other maintainability standards. However, BCH does use a 
representative benchmark of closed and open-source software projects to compute 
the thresholds for each maintainability guideline~\cite{Visser:2016:OREILLY, Baggen2012}.
Maintainability is computed as the mean of all guidelines. Different software versions 
(vulnerable/fixed) of one vulnerability may have the same overall score
and still be affected by different guidelines.
%
\\\textit{\textbf{Internal:}} The security patches dataset provided by previous
work~\cite{Reis:2017:IJSSE} was collected based on the messages of GitHub
commits produced by project developers to classify the changes performed while 
patching vulnerabilities. This approach discards patches that were
not explicit in commits messages. We assume that patches were performed 
using a single-commit or several sequentially. The view that a 
developer may perform a patch quickly and later proceed to the refactor is not considered.
Baseline commits are retrieved randomly from the same project of the security patch.
This approach softens the differences
that may result from the characteristics of each project. However,
maintainability may still be affected by the developers' experience, coding
style, and software contribution policies which are not evaluated in this study.
Furthermore, this evaluation considers that $969$ regular commits---any kind
of commit---are enough to
alleviate random irregularities in the maintainability differences of the
baseline. 
%
\\\textit{\textbf{External:}} We use a dataset that only comprises patches of open-source software.
However, the methodology requires to access data that is not publicly available.
Thus, our findings may not extend to non-open source software. Different programming 
languages may require different coding practices to address software safety. The 
dataset comprises more commits in Java, i.e., the dataset may not be representative 
of the population regarding programming languages. Our approach does not consider 
patches in any other language but English.
